---
title: "Vendor Analysis"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




# Libraries 
```{r}
library(readxl)
library(dplyr)
library(tidyr)
library(writexl)
```


# Load the data
```{r}
OP <- read_excel("Vendor_Prospects.xlsx")
TP <- read_excel("Transposed_VP.xlsx")
VP <- read_excel("Full_VP.xlsx")
CD <- read_excel("Noah - Connecting Data 20211020-094022.xlsx")
Combined_data <- left_join(by = "Ref",VP,CD)
```

# Change specific columns into factors
```{r}
Combined_data <- Combined_data %>%
  mutate(Admit = recode(Admit,
                        "1" = 1,
                        "0" = 0)) %>%
    mutate(Enrolled = recode(Enrolled,
                        "1" = 1,
                        "0" = 0))
```

# Create a binary column for if they applied and deposite date
```{r}
Combined_data<- Combined_data %>%
  mutate(Applied = ifelse(is.na(`App Submit Date`) == TRUE, 0,1)) %>%
  mutate(Deposited = ifelse(is.na(`Deposit Date`) == TRUE, 0,1))
```

# Transposed update with enrollement, admit, applied
```{r}
merging <- Combined_data %>%
  select(Ref,Enrolled,Admit,Applied,Deposited)
TP_full <- left_join(TP,merging,by = c("Ref" = "Ref"))
```


# Display the combined data
```{r}
head(Combined_data)
```

# How many people didnt get admitted but enrolled?
```{r}
Combined_data %>%
  mutate(no_ap_bt_enrl = ifelse(Admit == 0 & Enrolled == 1, 1,0) ) %>%
  group_by(no_ap_bt_enrl) %>%
  summarise(frequancy = n())


# There is three people who werent admitted but still enrolled?
# 151 na's
# I am going to filter out the outliers for my vendor analysis 
```

# Summary
```{r}
summary(Combined_data)
```






# What is the yield per vendor? (Percent of students that apply that get enrolled)
# What is the melt per vendor? (Percent of students that deposited but didnt enroll)
```{r}
Vendor_properies <- Combined_data %>%
  filter(!(Admit == 0 & Enrolled == 1)) %>%
  group_by(SourceFormat) %>%
  summarise(Yield = sum(Enrolled)/sum(Admit)*100, Melt = 100 - sum(Enrolled)/sum(Deposited)*100, prospects_2_applied = sum(Applied)/n()*100)

Vendor_properies
```

# We need the # of times each source occurs
```{r}
Total <- Combined_data %>%
  group_by(SourceFormat) %>%
  summarise(Total_Contact = n())
Total
```



# First Contact?
```{r}
TP1<- TP %>% 
  group_by(Source_1) %>%
  summarise(First_Contact = n())

TP2 <- TP %>%
  drop_na(Source_2) %>%
  group_by(Source_2) %>%
  summarise(Second_Contact = n())

TP3 <- TP %>%
  drop_na(Source_3) %>%
  group_by(Source_3) %>%
  summarise(Third_Contact = n())

TP4 <- TP %>%
  drop_na(Source_4) %>%
  group_by(Source_4) %>%
  summarise(Fourth_Contact = n())

TP5 <- TP %>%
  drop_na(Source_5) %>%
  group_by(Source_5) %>%
  summarise(Fifth_Contact = n())

TP_Final <- left_join(by = c("Source_1" = "Source_2"),TP1,TP2)
TP_Final <- left_join(by = c("Source_1" = "Source_3"),TP_Final,TP3)
TP_Final <- left_join(by = c("Source_1" = "Source_4"),TP_Final,TP4)
TP_Final <- left_join(by = c("Source_1" = "SourceFormat"),TP_Final,Total)
#TP_Final <- left_join(by = c("Source_1" = "Source_5"),TP_Final,TP5)

TP_Final[is.na(TP_Final)] <- 0
names(TP_Final)[1] <- "Sources"

TP_Final
```

# Download TP_Final
```{r}
# write_xlsx(TP_Final,"C:\\Users\\foilbn\\Documents\\Transposed_Contact.xlsx")
# write_xlsx(Vendor_properies,"C:\\Users\\foilbn\\Documents\\Vendor_Yield.xlsx")
```



# How effective is each vendor. 
```{r}
IP <- TP_Final %>%
  group_by(Sources) %>%
  summarise(First_Contact_Percent = round(First_Contact/Total_Contact *100,2),
         Second_Contact_Percent = round(Second_Contact/Total_Contact*100,2),
         Third_Contact_Percent = round(Third_Contact/Total_Contact*100,2),
         Fourth_Contact_Percent = round(Fourth_Contact/Total_Contact*100,2))
IP
```

# How about only percents per contact?
```{r}
ILP <- TP_Final %>%
  group_by(Sources) %>%
  summarise(Percent_1C = round(First_Contact/nrow(TP)*100,2),
            Percent_2C = round(Second_Contact/sum(TP_Final$Second_Contact),4)*100,
            Percent_3C = round(Third_Contact/sum(TP_Final$Third_Contact),4)*100,
            Percent_4C = round(Fourth_Contact/sum(TP_Final$Fourth_Contact),4)*100,
            Percent_Total = round(Total_Contact/sum(TP_Final$Total_Contact),4)*100)
ILP
```


# For tommorw look for duplicates? EX. Niche occurs multiple times in the vendor prospects. Look at that and see how many times a vendor sends us the same person. We paythem per vendor sometimes

# Duplicates?
```{r}
Duplicates <- OP %>%
  group_by(Ref,SourceFormat) %>%
  summarise(Frequancy = n()) %>%
  arrange(desc(Frequancy)) %>%
  filter(Frequancy != 1) %>%
  mutate(Frequancy = Frequancy - 1) %>%
 arrange(desc(Frequancy)) %>%
  group_by(SourceFormat) %>%
  summarise(Total_Duplicates = sum(Frequancy))
```

# Find a good way to diplay such data
```{r}
T<- OP %>%
  group_by(SourceFormat) %>%
  summarise(Total_Occurences = n())
```

# Final
```{r}
DP <- left_join(by = c("SourceFormat" = "SourceFormat"),T,Duplicates)
```

# Percents?
```{r}
DP <- DP %>% 
  mutate(Percent_Duplicates = round(Total_Duplicates/Total_Occurences*100,2))
DP
# Look at ref 024297179
```

# Joining data 
```{r}
Duplicate_Final <- left_join(by = c("SourceFormat" = "Sources"),DP,IP)
```

# Download Duplicate_Final
```{r}
write_xlsx(Duplicate_Final,"C:\\Users\\foilbn\\Documents\\Duplicate_Final.xlsx")
write_xlsx(IP,"C:\\Users\\foilbn\\Documents\\IP.xlsx")
write_xlsx(ILP,"C:\\Users\\foilbn\\Documents\\ILP.xlsx")
```


#Relationship between the amount of sources find a reference vs their enrollment rate. Ex: ppl who are found 4 times are more likely to enroll vs 3 vs 2 vs 1 
```{r}
Contacted_Once <- TP_full[is.na(TP_full$Source_2), ]
C1 <- Contacted_Once %>%
  filter(!(Admit == 0 & Enrolled == 1)) %>%
  drop_na(Source_1) %>%
  summarise(Contact = "Contacted Once", Yield = sum(Enrolled)/sum(Admit)*100, Melt = 100 - sum(Enrolled)/sum(Deposited)*100, prospects_2_applied = sum(Applied)/n()*100)

Contacted_Twice <- TP_full[is.na(TP_full$Source_3), ]
C2 <- Contacted_Twice %>%
  filter(!(Admit == 0 & Enrolled == 1)) %>%
  drop_na(Source_2) %>%
  summarise(Contact = "Contacted Twice", Yield = sum(Enrolled)/sum(Admit)*100, Melt = 100 - sum(Enrolled)/sum(Deposited)*100, prospects_2_applied = sum(Applied)/n()*100)

Contacted_Thrice <- TP_full[is.na(TP_full$Source_4), ]
C3 <- Contacted_Thrice %>%
  filter(!(Admit == 0 & Enrolled == 1)) %>%
  drop_na(Source_3) %>%
  summarise(Contact = "Contacted Thrice", Yield = sum(Enrolled)/sum(Admit)*100, Melt = 100 - sum(Enrolled)/sum(Deposited)*100, prospects_2_applied = sum(Applied)/n()*100)

C4 <- TP_full %>%
  filter(!(Admit == 0 & Enrolled == 1)) %>%
  drop_na(Source_4) %>%
  summarise(Contact = "Contacted Frice", Yield = sum(Enrolled)/sum(Admit)*100, Melt = 100 - sum(Enrolled)/sum(Deposited)*100, prospects_2_applied = sum(Applied)/n()*100)

CT <- rbind(C1,C2,C3,C4)
CT
```


# Download CT
```{r}
#write_xlsx(CT,"C:\\Users\\foilbn\\Documents\\Contact_Efficency .xlsx")

```









