---
title: "Names"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Libraries
```{r}
library(readxl)
library(dplyr)
library(stringr)
library(writexl)
library(rlang)
```


# Loading in the Data
```{r}
#raw_data <- read_excel("Preferred Name QA_QC 20211007-090939.xlsx")
raw_data <- read_excel("Quick Query 20220322-142208.xlsx")
clean_data <- raw_data
```


# Creation of the function that will find common errors in a dataset
```{r}
Uncleaned <- function(Raw_data,Column_Name) {                                   # Creation of function 
df1 <- Raw_data%>%                                                              # I created this first dataset to filter for the peple who have an unknown character 
    filter(str_detect(Column_Name,"1|2|3|4|5|6|7|8|9|0|\\(|\\)")) %>%           
    mutate(Reason_4_Review = "Unknown Character")
df2 <- Raw_data%>%                                                              # I created this second dataset to find the people who have an "or" or a ","
    filter(str_detect(Column_Name," or |,")) %>%
    mutate(Reason_4_Review = "Or/,")
Return <- union(df1,df2)                                                        # I combined the data
  return(Return)
}

Length_Check <- function(Raw_data,Column_Name){
df1 <- Raw_data%>%                                                               
    filter(str_length(Column_Name) > 12) %>%           
    mutate(Reason_4_Review = "Greater than 12 characters")
}
```



# Finding the data that needs to be clean
```{r}
Needs_Review_p <- Uncleaned(raw_data,raw_data$Preferred) %>%                    # Execution of the data through the function
  mutate(Error_Location = "Preferred")
Needs_Review_f <- Uncleaned(raw_data,raw_data$First)  %>%                        
  mutate(Error_Location = "First")
Needs_Review_m <- Uncleaned(raw_data,raw_data$Middle)%>%                       
  mutate(Error_Location = "Middle")
Needs_Review_l <- Uncleaned(raw_data,raw_data$Last)%>%                        
  mutate(Error_Location = "Last")
Needs_Review_length_p <- Length_Check(raw_data,raw_data$Preferred) %>%
  mutate(Error_Location = "Preferred")

#Needs_review_pfl <- clean_data%>%          #This was to find when when the preferred name consisted of the first name plus last name. 
  #filter(str_detect(Preferred, First)) #%>%
  #filter(str_detect(Preferred, Last)) %>%
  #mutate(Reason_4_Review = "Preferred = First+Last Name")

Needs_review <- bind_rows(Needs_Review_length_p,Needs_Review_f,Needs_Review_l,Needs_Review_m,Needs_Review_p)   # Combining the data so all the uncleaned data is in one place. 
```

#Exporting data
```{r}
#write_xlsx(Needs_review,"C:\\Users\\foilbn\\Documents\\R workspace\\Needs_review.xlsx")              #This exports the data as a excel file. 
```

# Preferred Name if unexpected number
```{r}
Fixed_Pre <- Needs_Review_p %>%
  filter(str_detect(Preferred,"1|2|3|4|5|6|7|8|9|0")) %>%
  mutate(Preferred = First)

clean_data <- full_join(clean_data,Fixed_Pre)%>%
  filter(str_detect(Preferred,"1|2|3|4|5|6|7|8|9|0") == FALSE)
```

# Preferred Name if format: First(Preferred)
```{r}

```

# Preferred Name if 
```{r}
#Fixed_pfl <- clean_data%>%    
 # filter(str_detect(Preferred," or ")) %>%
  #filter(str_detect(Preferred, First)) %>%
  #filter(str_detect(Preferred, Last)) %>%
  #mutate(Preferred = First)

#Tst <- full_join(clean_data,Fixed_pfl)#%>%
 # filter(!str_detect(Preferred, First) == FALSE  & !str_detect(Preferred, Last) == FALSE)
  

#clean_data[str_detect(clean_data$Preferred,clean_data$Last)] #<- Fixed_pfl$Preferred 
```






# Middle Name

```{r}
raw_data %>%
  filter(str_length(raw_data$Preferred)>12)
```



# Creation of the cleaning function 
```{r}
Cleaned <- function(Raw_data, Needs_review, Column_Name) {
  
Raw_data %>%
 filter(str_detect(Column_Name,"1|2|3|4|5|6|7|8|9|0")) %>%           
    mutate(Column_Name, )
    
Raw_data %>% 
    filter()
  
  
  
  
  
}
  
  
  
  
```








# Cleaning the data
```{r}
Cleaning <- function(Unclean_Dataset,Column_Name){
  Unclean_Dataset %>%
    filter(str_detect(Column_Name,"1|2|3|4|5|6|7|8|9|0")) %>%
  mutate(Column_Name = NA)
}

```

# Cleaning the data
```{r}
#Fixed_Pre <- uncleaned_Pre %>%
#  filter(str_detect(Preferred,"1|2|3|4|5|6|7|8|9|0")) %>%
#  mutate(Preferred = NA)

#clean_data <- full_join(clean_data,Fixed_Pre)%>%
#  filter(str_detect(Preferred,"1|2|3|4|5|6|7|8|9|0") == FALSE | is.na(Preferred) == TRUE)




#Fixed_Mid <- uncleaned_Mid %>%
#  filter(str_detect(Middle,"1|2|3|4|5|6|7|8|9|0")) %>%
#  mutate(Middle = NA)

#clean_data <- full_join(clean_data,Fixed_Mid)%>%
#  filter(str_detect(Middle,"1|2|3|4|5|6|7|8|9|0") == FALSE | is.na(Middle) == TRUE)
```



#Luiza Acioly - look her frist name and last name
# I need to fix the () and "" issue for reusability
# Ned to clean the data for a theoretical missinput for last name and first name 
# For 


















