---
title: "Vendor Prospects Testing"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Libraries 
```{r}
library(readxl)
library(dplyr)
library(tidyr)
library(writexl)
```


# Load the data
```{r}
NACAC <- read_excel("NACAC College Fair Lists Prospect Records.xlsx")
College_Board <- read_excel("College Board Search Name Buy Prospect Records.xlsx")
PCU <- read_excel("PCU Prospect Records.xlsx")
Niche <- read_excel("Niche Lead Delivery Prospect Records.xlsx")
Active_Match <- read_excel("Active Match + Prospect Records.xlsx")

Vendor_Prospects <- bind_rows(NACAC,College_Board,PCU,Niche,Active_Match)
```


# Create Function to Split the Recd into date and time and sort the data. Then get rid of duplicates
```{r}
TimeSplit <- function(DataFrame) {
  Result <- DataFrame %>%
    mutate(TimeRecd = substr(DateRecd,12,nchar(DateRecd))) %>%
    mutate(DateRecd = as.Date(substr(DateRecd,1,10), "%m/%d/%Y")) %>%
    arrange(Ref,DateRecd)
  Result <- Result[!duplicated(Result$Ref), ]

  return(Result)
}
```


# Fixed the data
```{r}
NACAC_Clean <- TimeSplit(NACAC)
College_Board_Clean <- TimeSplit(College_Board)
PCU_Clean <- TimeSplit(PCU)
Niche_Clean <- TimeSplit(Niche)
Active_Match_Clean <- TimeSplit(Active_Match)  

Vendor_Prospects_Clean <- bind_rows(NACAC_Clean, College_Board_Clean, PCU_Clean, Niche_Clean, Active_Match_Clean) %>%
  arrange(Ref,DateRecd)

```

# Exporting data
```{r}
#write_xlsx(Vendor_Prospects_Clean,"C:\\Users\\foilbn\\Documents\\Vendor_Prospects.xlsx")
```


# Plan of action: Create five columns for five sources. Source 1 is the first vendor who reached out to the prospect
```{r}
V <- Vendor_Prospects_Clean %>%
  select(Ref,SourceFormat,DateRecd,TimeRecd)

reshape(V, timevar = "SourceFormat",idvar = "Ref", direction = "wide")




```


```{r}
# Initial conditions

A = 0
I = 50
# Create the source columns
Vendor_Prospects_Clean <- Vendor_Prospects_Clean %>%
  mutate(Source_1 = NA, Source_1_Date = NA, Source_2 = NA, Source_2_Date = NA, Source_3 = NA, Source_3_Date = NA,Source_4 = NA, Source_4_Date = NA,Source_5 = NA, Source_5_Date = NA)
Vendor_final <- Vendor_Prospects_Clean
Vendor_final$SourceFormat <- NULL
Vendor_final$DateRecd <- NULL


for (i in 1:nrow(Vendor_Prospects_Clean)) {
  ID = Vendor_Prospects_Clean[i,1]
  if (Vendor_Prospects_Clean[I,1] == ID) {
    A = A + 1
    if (A == 2) {
        Vendor_final[I,18] = Vendor_Prospects_Clean[i,3]
        Vendor_final[I,19] = Vendor_Prospects_Clean[i,4]
    }else {
      if (A ==3) {
        Vendor_final[I,20] = Vendor_Prospects_Clean[i,3]
        Vendor_final[I,21] = Vendor_Prospects_Clean[i,4]
      }else {
        if (A==4) {
          Vendor_final[I,22] = Vendor_Prospects_Clean[i,3]
          Vendor_final[I,23] = Vendor_Prospects_Clean[i,4]
        }else {
          Vendor_final[I,24] = Vendor_Prospects_Clean[i,3]
          Vendor_final[I,25] = Vendor_Prospects_Clean[i,4]
        }
      }
    }
  } else {
    ID = Vendor_Prospects_Clean[i,1]
    A = 1
    I = i   # In order to remember the first instance of the Row ID
    Vendor_final[I,16] = Vendor_Prospects_Clean[I,3]
    Vendor_final[I,17] = Vendor_Prospects_Clean[I,4]
  }
  
#  if (i%%5000 == 0) {
#    print(i)
#  }
  
  
  }


```

# Fix the data so we only have the final rows
```{r}
Vendor_final <- Vendor_final %>%
  drop_na(Source_1)
```


# Exporting data
```{r}
#write_xlsx(Vendor_final,"C:\\Users\\foilbn\\Documents\\Vendor_final.xlsx")
```



# How many people have reoccuring Refs?
```{r}
T <- Vendor_Prospects_Clean %>%
 # filter(SourceFormat == "Niche Lead Delivery") %>%
  group_by(Ref) %>%
  summarise(num_vendors = n())
 # arrange(desc(num_vendors)) %>%
#  group_by(num_vendors) %>%
 # summarise(Num_occ = n())
nrow(T)
```

# Individual search
```{r}
Ind <- Vendor_Prospects_Clean %>%
  filter(Ref == 037500275) 
  
Ind
```

```{r}
Vendor_Prospects_Clean %>%
  group_by(Ref) %>%
  summarise(frequancy = n()) %>%
  arrange(desc(frequancy))
```















